Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-02 journal/article.tex
Spell check

Based on the primary studies we identified two dimensions in the characteristics
of transformation processes. The first dimension is the pivot point of
leadership in change. This dimension has two extremes: top-down leadership where
the change is mandated by management, and bottom-up leadership where the chage
emerges from team level. The second dimension is the velocity of the change.
Organizations were reported to perform transformations as a big bang or
overnight fashion, or as a step wise process lasting for a long time. Figure
\ref{fig:transformation_dimensions} summarizes the transformation process
dimensions.

@@

We do not quantitively measure cases on the transformation process dimensions,
because the criteria for creating a measurement would be vague. For instance, we
do not think that presenting a single quantitative measurement of the weight
point of leadership on an axis between management centric and team centric would
describe reality accurately. The dimensions of pivot of leadership and
transformation velocity nevertheless exist.

@@

The most extreme case of adoption was a bing bang transformation. To realize
such a large change it is necessary that the change was centrally coordinated.
For step wise transformations there were three variants depending on the amount
of involvement of management and development teams. In some cases teams palyed a
passive role, and in some cases management was described to be reluctant to
change. In many cases both management and devlopment dealed with the
transformation on their respective level of influence.

As a concept separate from the dimensions of leadership pivot and velocity, the
transformation was described as a continuous process. There were a few
viewpoints illustrating the concept of continuous transformation. Several
organizations strived to introduce a culture of continuous improvement, which
would make organizational adjustment a permanent state. In many cases the agile
transformation was not considered to have ended at any distinct point in time,
and the impression that it was still ongoing was given. Finally, transformation
was simply described as hard work that will inevitably take a long time.

@@

There was some variance of approaches in choosing the pilot projects.
In some cases the project or teams to pilot the agile methods were chosen
carefully [P7, P8, P38, P40], but others chose the pilot teams from volunteers
[P9, P10, P45].
Some organizations considered it important to pilot agile with business critical
projects, as the applicability had to be proven in a releant environment [P8,
P40].

@@

% What other things did the pilot teach?
There were still a few particular insights regarding use of piloting.
Fry and Greene [P16] describe a particular big bang adoption where piloting was
omitted. A pilot project was avioded because having two models side by side was
deemed to create organizational dissonance. Instead a significant amout of
people completed agile training and the new model was introduced overnight
[P16].
In some cases the success of the pilot gave unrealistic expectations [P38, P45].
Organizations should beware if the team is set up of all-star developers, as
the results will likely be much better than average [P38].

@@

It was very typical that external help was brought in to help with the
transformation.
External consultants were employed especially at the start of the
transformation. At the time it was realized that the way of working should be
changed a consultant was often hired to assess the current state and give a
recommendation on how to proceed [P16, P20, P41, P43, P41, P44, P51].
In the beginning external consultants were used to ignite interest in agile
methods, and provide initial education [P7, P9, P27, P30, P43].
It was recommended to bring in extenal help as early as possible, when the
internal agile expertise is lacking and before transformation challenges appear
[P6, P16, P30].

When the transformation was getting on its way, agile consultants were typically
leading training sessions, arranging agile workshops, and coaching teams.
In some cases consultants helped specifically with scaling up the use of agile
beyond single teams [P31, P34].
Consultants were used mostly in the first stages of the transformation.
The need for external consultants reduced over time, and their tasks were
transfered to internal positions [P29, P47].
It was described that as the agile journey progressed, external consultants were
invited every now and then to bring in fresh ideas to the organization [P6].

@@

* It is difficult to distinguish between team and organization. In most cases
  when talking about teams it refers to a handfull of people familiar to each
  other. However, in some cases it was evident that an entire department was
  referred to as a team.

>>>>

Based on the primary studies we identified two dimensions in the characteristics
of transformation processes. The first dimension is the pivot point of
leadership in change. This dimension has two extremes: top-down leadership where
the change is mandated by management, and bottom-up leadership where the change
emerges from team level. The second dimension is the velocity of the change.
Organizations were reported to perform transformations as a big bang or
overnight fashion, or as a step wise process lasting for a long time. Figure
\ref{fig:transformation_dimensions} summarizes the transformation process
dimensions.

@@

We do not quantitatively measure cases on the transformation process dimensions,
because the criteria for creating a measurement would be vague. For instance, we
do not think that presenting a single quantitative measurement of the weight
point of leadership on an axis between management centric and team centric would
describe reality accurately. The dimensions of pivot of leadership and
transformation velocity nevertheless exist.

@@

The most extreme case of adoption was a big bang transformation. To realize
such a large change it is necessary that the change was centrally coordinated.
For step wise transformations there were three variants depending on the amount
of involvement of management and development teams. In some cases teams played a
passive role, and in some cases management was described to be reluctant to
change. In many cases both management and development dealt with the
transformation on their respective level of influence.

As a concept separate from the dimensions of leadership pivot and velocity, the
transformation was described as a continuous process. There were a few
viewpoints illustrating the concept of continuous transformation. Several
organizations were striving to introduce a culture of continuous improvement, which
would make organizational adjustment a permanent state. In many cases the agile
transformation was not considered to have ended at any distinct point in time,
and the impression that it was still ongoing was given. Finally, transformation
was simply described as hard work that will inevitably take a long time.

@@

There was some variance of approaches in choosing the pilot projects.
In some cases the project or teams to pilot the agile methods were chosen
carefully [P7, P8, P38, P40], but others chose the pilot teams from volunteers
[P9, P10, P45].
Some organizations considered it important to pilot agile with business critical
projects, as the applicability had to be proven in a relevant environment [P8,
P40].

@@

% What other things did the pilot teach?
There were still a few particular insights regarding use of piloting.
Fry and Greene [P16] describe a particular big bang adoption where piloting was
omitted. A pilot project was avoided because having two models side by side was
deemed to create organizational dissonance. Instead a significant amount of
people completed agile training and the new model was introduced overnight
[P16].
In some cases the success of the pilot gave unrealistic expectations [P38, P45].
Organizations should beware if the team is set up of all-star developers, as
the results will likely be much better than average [P38].

@@

It was very typical that external help was brought in to help with the
transformation.
External consultants were employed especially at the start of the
transformation. At the time it was realized that the way of working should be
changed a consultant was often hired to assess the current state and give a
recommendation on how to proceed [P16, P20, P41, P43, P41, P44, P51].
In the beginning external consultants were used to ignite interest in agile
methods, and provide initial education [P7, P9, P27, P30, P43].
It was recommended to bring in external help as early as possible, when the
internal agile expertise is lacking and before transformation challenges appear
[P6, P16, P30].

When the transformation was getting on its way, agile consultants were typically
leading training sessions, arranging agile workshops, and coaching teams.
In some cases consultants helped specifically with scaling up the use of agile
beyond single teams [P31, P34].
Consultants were used mostly in the first stages of the transformation.
The need for external consultants reduced over time, and their tasks were
transferred to internal positions [P29, P47].
It was described that as the agile journey progressed, external consultants were
invited every now and then to bring in fresh ideas to the organization [P6].

@@

* It is difficult to distinguish between team and organization. In most cases
  when talking about teams it refers to a handful of people familiar to each
  other. However, in some cases it was evident that an entire department was
  referred to as a team.
